Autonomous Oceanographic Data Collection Estimating Excursion Sets of Vector-valued Gaussian Random Fields

### 2020-06-22 main_new.tex
Updates from Overleaf

\begin{figure}[h!] \centering
  \includegraphics[width=0.99\textwidth]{Figures/example_excu_1.png}
  \caption{Realization of a bivariate GRF and excursion set above some
    threshold ({\kc{JE: are means around 5 and 30 here, so same as
        later in the example?}} ). Joint excursion in red, excursion
    of a single variable in pink.}
\label{example_excu}
\end{figure}

@@

Assuming that $n$ batches of observations are available, with respective sizes $q_1,\dots, q_n$, and that one wishes 
to predict $\gp[\bm{x}]$ for some batch of $q\geq 1$ generalized locations $\bm{x}$, %\equiv(\bm{\spatloc}, \bm{\ell})$, 
the (simple) cokriging mean then amounts to kriging with respect to a scalar-valued GRF indexed by 
$\domain\times \{1\dots,p\}$:  
%
\begin{equation}\label{eq:cokrig_mean}
\mu_{[n]}(\bm{x})=\mu(\bm{x})+\lambda_{[n]}(\bm{x})^T (\mathbf{z}_{[n]}-\mu(\bm{x})),
\end{equation}
where $\mu$ is $Z$'s initial mean function, $\mathbf{z}_{[n]}$ stands for the ($\sum_{i=1}^n q_i$)-dimensional vector of observed (noisy) responses of $Z$ at all considered generalized locations, and $\lambda_{[n]}(\bm{x})$ is a vector of weights
equal to $\widetilde{\bm{K}_{[0,n]}}^{-1} k(\bm{x}_{[n]}, \bm{x})$ with $\bm{x}_{[n]}=(\bm{x}_1,\dots, \bm{x}_n)$ and $\widetilde{\bm{K}_{[0,n]}}=k(\bm{x}_{[n]}, \bm{x}_{[n]})+\Delta_{[n]}$, assumed non-singular throughout the presentation, where $\Delta_{[n]}$ stands for the covariance matrix of Gaussian-distributed noise assumed to have affected measurements up to batch $n$. The co-kriging %(conditional) 
residual (cross-)covariance function (with respect to batches of generalized locations) can also be expressed in the same vein via
%
\begin{equation}\label{eq:cokrig_cov}
k_{[n]}(\bm{x},\bm{x}')=k(\bm{x},\bm{x}')-\lambda_{[n]}(\bm{x})^T \widetilde{\bm{K}_{[0,n]}} \lambda_{{[n]}}(\bm{x}').
\end{equation}

>>>>

\begin{figure}[h!] \centering
  \includegraphics[width=0.99\textwidth]{Figures/example_excu_4.png}
  \caption{Realization of a bivariate GRF and excursion set above some
    threshold ({\kc{JE: are means around 5 and 30 here, so same as
        later in the example?}} ). Joint excursion in red, excursion
    of a single variable in pink.}
\label{example_excu}
\end{figure}

@@

Assuming that $n$ batches of observations are available, with respective sizes $q_1,\dots, q_n$, and that one wishes 
to predict $\gp[\bm{x}]$ for some batch of $q\geq 1$ generalized locations $\bm{x}$, %\equiv(\bm{\spatloc}, \bm{\ell})$, 
the (simple) cokriging mean then amounts to kriging with respect to a scalar-valued GRF indexed by 
$\domain\times \{1\dots,p\}$:  
%
\begin{equation}\label{eq:cokrig_mean}
\mu_{[n]}(\bm{x})=\mu(\bm{x})+\lambda_{[n]}(\bm{x})^T (\mathbf{z}_{[n]}-\mu(\bm{x})),
\end{equation}
where $\mu$ is $Z$'s initial mean function, $\mathbf{z}_{[n]}$ stands for the ($\sum_{i=1}^n q_i$)-dimensional vector of observed (noisy) responses of $Z$ at all considered generalized locations, and $\lambda_{[n]}(\bm{x})$ is a vector of weights
equal to 
$$\left(k(\bm{x}_{[n]}, \bm{x}_{[n]})+\Delta_{[n]} \right)^{-1} k(\bm{x}_{[n]}, \bm{x})
$$
with $\bm{x}_{[n]}=(\bm{x}_1,\dots, \bm{x}_n)$ and where $\Delta_{[n]}$ stands for the covariance matrix of Gaussian-distributed noise assumed to have affected measurements up to batch $n$. The matrix in parenthesis in the above equation will be assumed non-singular throughout the presentation. The co-kriging %(conditional) 
residual (cross-)covariance function (with respect to batches of generalized locations) can also be expressed in the same vein via
%
\begin{equation}\label{eq:cokrig_cov}
k_{[n]}(\bm{x},\bm{x}')=k(\bm{x},\bm{x}')-\lambda_{[n]}(\bm{x})^T 
\left(k(\bm{x}_{[n]}, \bm{x}_{[n]})+\Delta_{[n]} \right)
\lambda_{{[n]}}(\bm{x}').
\end{equation}
